Bird beak's elaboration and innovation

### 2021-11-26 Analysis/03.1-results.Rmd
Update 03.1-results.Rmd

```{r, eval = TRUE, echo = TRUE}
## Load the data
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.rda")
## Select the data
shapespace <- shapespace_allbirds_lvl_superorder_order[[1]]$space
tree <- shapespace_allbirds_lvl_superorder_order[[1]]$consensus_tree

@@

order_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(order_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level2)[-1], "phylogeny")) #[-1] is because the first level is ""
```

@@

```{r, echo = FALSE, fig.height = 14, fig.width = 14, eval = TRUE}
par(mfrow = c(2,2))
## Plotting mean axes
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average ellipses by super order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average major axes by super order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
## Plotting mean axes
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average ellipses by order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average major axes by order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
```

@@

    ## Plot
    covar.plot(sub, major.axes = TRUE, ellipses = TRUE, points = FALSE, legend = FALSE, main = main)
    covar.plot(sub, major.axes = mean, ellipses = mean, points = FALSE, col = "red", add = TRUE)
}

@@

```{r, echo = FALSE}
## Quick load
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list_uncentred.rda")
results_cent <- shapespace_allbirds_lvl_superorder_order_results_list
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
```

@@

    ## Add the relative results
    if(add.relative) {
        make.relative <- function(X) {
            cbind(X, "rel" = ifelse(is.na(X$score), NA, X$score/max(X$score)))
        }
        output <- lapply(output, make.relative)
    }
    return(output)
}
combine.results <- function(res1, res2, sort.results = TRUE) {
    ## Combine the results
    res_out <- rbind(res1[,1:2], res2[, 1:2])
    res_out$elaboration <- c(res1[, 3], rep(NA, nrow(res2)))
    if("rel" %in% colnames(res1)) {
        res_out$rel.elab <- c(res1[, 4], rep(NA, nrow(res2)))
    }
    res_out$innovation <- c(rep(NA, nrow(res1)), res2[, 3])
    if("rel" %in% colnames(res1)) {
        res_out$rel.inno <- c(rep(NA, nrow(res1)), res2[, 4])
    }

>>>>

```{r, eval = TRUE, echo = TRUE}
## Load the data
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order.rda")
## Select the data
shapespace <- shapespace_allbirds_lvl_superorder_order[[1]]$space
tree <- shapespace_allbirds_lvl_superorder_order[[1]]$consensus_tree
## Clean garbage
rm(shapespace_allbirds_lvl_superorder_order)

@@

order_shapespace <- MCMCglmm.subsets(
      data          = shapespace,
      posteriors    = shapespace_allbirds_lvl_superorder_order,
      group         = MCMCglmm.levels(shapespace_allbirds_lvl_superorder_order)[c(order_lvl, phylo_lvl)],
      rename.groups = c(levels(shapespace$level2)[-1], "phylogeny")) #[-1] is because the first level is ""
## Clean garbage
rm(shapespace_allbirds_lvl_superorder_order)
```

@@

```{r, echo = FALSE, fig.height = 14, fig.width = 14, eval = TRUE}
par(mfrow = c(2,2))
## Plotting mean axes
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average ellipses by super order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(superorder_shapespace,
           col = c(rainbow(n.subsets(superorder_shapespace)-1), "grey"),
           main = "Average major axes by super order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average ellipses by order",
           ellipses = mean,
           legend = FALSE,
           points = FALSE,
           cex = 0.5)
## Plotting mean ellipses
covar.plot(order_shapespace,
           col = c(rainbow(n.subsets(order_shapespace)-1), "grey"),
           main = "Average major axes by order",
           major.axes = mean,
           legend = TRUE,
           points = FALSE,
           cex = 0.5)
```

@@

    ## Plot
    covar.plot(sub, major.axes = TRUE, ellipses = TRUE, points = FALSE, legend = FALSE, main = main)
    covar.plot(sub, major.axes = mean, ellipses = mean, points = FALSE, col = "red", add = TRUE)
    rm(sub)
}

@@

```{r, echo = FALSE}
## Quick load
# load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list_uncentred.rda")
# results_cent <- shapespace_allbirds_lvl_superorder_order_results_list
load(file = "../Data/Processed/shapespace_allbirds_lvl_superorder_order_results_list.rda")
results <- shapespace_allbirds_lvl_superorder_order_results_list
rm(shapespace_allbirds_lvl_superorder_order_results_list)
```

@@

    ## Add the relative results
    if(add.relative) {
        make.relative <- function(X) {
            cbind(X, "rel" = ifelse(is.na(X$score), NA, X$score/max(X$score)))
        }
        output <- lapply(output, make.relative)
    }
    rm(disparity)
    return(output)
}
combine.results <- function(res1, res2, sort.results = TRUE) {
    ## Combine the results
    res_out <- rbind(res1[,1:2], res2[, 1:2])
    res_out$elaboration <- c(res1[, 3], rep(NA, nrow(res2)))
    if("rel" %in% colnames(res1)) {
        res_out$rel.elab <- c(res1[, 4], rep(NA, nrow(res2)))
    }
    res_out$innovation <- c(rep(NA, nrow(res1)), res2[, 3])
    if("rel" %in% colnames(res1)) {
        res_out$rel.inno <- c(rep(NA, nrow(res1)), res2[, 4])
    }
